---
title: 'BG_report for Dates: 2019-10-24 to 2019-10-28'
author: "Lillian Gorman Sanisaca, rscmb_c3@yahoo.com"
date: "`r paste0('Report Generated : ',format(Sys.time(), '%m-%d-%Y'))`"
output: html_document
params:
  libraryPath: libraryPath
  filePath: filePath
  numberDays: numberDays
  fromChange: fromChange
  startDate: startDate
  endDate: endDate
  removeDates: removeDates
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.width=12, fig.height=8, warning = FALSE)
```


```{r, eval=TRUE, echo=FALSE,warning=FALSE, message = FALSE}
#setPaths
libraryPath<-params$libraryPath
filePath<-params$filePath
numberDays<-params$numberDays
fromChange<-params$fromChange
startDate<-params$startDate
endDate<-params$endDate
removeDates<-params$removeDates

changeParam.list = list(fromChange = fromChange,
                        startDate = startDate,
                        endDate = endDate,
                        removeDates = removeDates)

#load functions
suppressWarnings(suppressMessages(devtools::load_all(libraryPath,recompile = FALSE)))

#get pumpSettings
pumpSettings.list<-makePumpSettings(libraryPath)
unPackList(lists = list(pumpSettings.list = pumpSettings.list),
           parentObj = list(NA)) 

#metronic csv data import
dataImport.list<-dataImport(filePath,libraryPath)
unPackList(lists = list(dataImport.list = dataImport.list),
           parentObj = list(NA)) 


#summarize data
BGvalue_Summary<-summarizeData(allData, colName = "BG.Reading..mg.dL.", libraryPath = libraryPath,
                               fromChange = fromChange,startDate = startDate,
                               endDate = endDate,removeDates = removeDates)
Sensorvalue_Summary<-summarizeData(allData, colName = "Sensor.Glucose..mg.dL.", libraryPath = libraryPath,
                               fromChange = fromChange,startDate = startDate,
                               endDate = endDate,removeDates = removeDates)

BGvalue_SummaryDaily<-summarizeData(allData, colName = "BG.Reading..mg.dL.",  timeStep = "day", 
                                    libraryPath = libraryPath,fromChange = fromChange,startDate = startDate,
                                    endDate = endDate,removeDates = removeDates)
BGpercent_Summary<-addPercentBG_ly(data = allData, p = NA,addPercentBG = c("very high","high","good","low"),
                                   addPercentType = "BG.Reading..mg.dL.",outputType = "table",
                                   libraryPath = libraryPath,fromChange = fromChange,startDate = startDate,
                                   endDate = endDate,removeDates = removeDates)
SGpercent_Summary<-addPercentBG_ly(data = allData, p = NA,addPercentBG = c("very high","high","good","low"),
                                   addPercentType = "Sensor.Glucose..mg.dL.",outputType = "table",
                                   libraryPath = libraryPath,fromChange = fromChange,startDate = startDate,
                                   endDate = endDate,removeDates = removeDates)
BGHigh_Count<-summarizeData(allData, colName = "BG.Reading..mg.dL.", 
                            sumFuncs = "length",
                            filterCond = "data[data$BG.Reading..mg.dL.>150 & !is.na(data$BG.Reading..mg.dL.),]",
                            libraryPath = libraryPath,fromChange = fromChange,startDate = startDate,
                            endDate = endDate,removeDates = removeDates)
BGveryHigh_Count<-summarizeData(allData, colName = "BG.Reading..mg.dL.", 
                                sumFuncs = "length",
                                filterCond = "data[data$BG.Reading..mg.dL.>240 & !is.na(data$BG.Reading..mg.dL.),]",
                                libraryPath = libraryPath,fromChange = fromChange,startDate = startDate,
                                endDate = endDate,removeDates = removeDates)

BGLow_Count<-summarizeData(allData, colName = "BG.Reading..mg.dL.", 
                           sumFuncs = "length",
                           filterCond = "data[data$BG.Reading..mg.dL.<80 & !is.na(data$BG.Reading..mg.dL.),]",
                           libraryPath = libraryPath,fromChange = fromChange,startDate = startDate,
                           endDate = endDate,removeDates = removeDates)
BGgood_Count<-summarizeData(allData, colName = "BG.Reading..mg.dL.", 
                            sumFuncs = "length",
                            filterCond = "data[data$BG.Reading..mg.dL.>=80 & data$BG.Reading..mg.dL.<=150 & !is.na(data$BG.Reading..mg.dL.),]",
                            libraryPath = libraryPath,fromChange = fromChange,startDate = startDate,
                            endDate = endDate,removeDates = removeDates)
tempBasal_count<-summarizeData(allData, colName = "Temp.Basal.Amount", 
                               sumFuncs = "length",
                               filterCond = "data[data$Temp.Basal.Amount==0 & !is.na(data$Temp.Basal.Amount),]",
                               libraryPath = libraryPath,fromChange = fromChange,startDate = startDate,
                               endDate = endDate,removeDates = removeDates)
suspendBasal_Count<-summarizeData(allData, colName = "Alarm", 
                                  sumFuncs = "length",
                                  filterCond = "data[regexpr('SUSPEND',data$Alarm)>0 & !is.na(data$Alarm),]", 
                                  libraryPath = libraryPath,fromChange = fromChange,startDate = startDate,
                                  endDate = endDate,removeDates = removeDates)


#timeDayTables used for heatmaps
BGvalue_timeDaytable<-timeDayTable(allData, tcol = "time2", dcol = "Date2", 
                                   valueVar = "BG.Reading..mg.dL.", 
                                   sumFunc = "mean", naRemove = TRUE,
                                   includeTotals = TRUE,
                                  filterCond = "",
                                   libraryPath = libraryPath,fromChange = fromChange,startDate = startDate,
                                  endDate = endDate,removeDates = removeDates)
SGvalue_timeDaytable<-timeDayTable(allData, tcol = "time2", dcol = "Date2", 
                                   valueVar = "Sensor.Glucose..mg.dL.", 
                                   sumFunc = "mean", naRemove = TRUE,
                                   includeTotals = TRUE,
                                   filterCond = "",
                                   libraryPath = libraryPath,fromChange = fromChange,startDate = startDate,
                                   endDate = endDate,removeDates = removeDates)


```

##BG value stats by hour
```{r, eval=TRUE}
BGvalue_Summary
```
##BG value stats by day
```{r, eval=TRUE}
BGvalue_SummaryDaily
```

##Sensor value stats by hour
```{r, eval=TRUE}
Sensorvalue_Summary
```

##BG high (>150) count
```{r, eval=TRUE}
BGHigh_Count
```

##BG very high (>240) count
```{r, eval=TRUE}
BGveryHigh_Count
```

##BG low (<80) count
```{r, eval=TRUE}
BGLow_Count
```

##BG good value count (>80 and <150)
```{r, eval=TRUE}
BGgood_Count
```

##Temp Basal = 0 count
```{r, eval=TRUE}
tempBasal_count
```

##Suspend basal on low count
```{r, eval=TRUE}
suspendBasal_Count
```


##BG value by time and date with mean values
```{r, eval=TRUE,fig.width=10, fig.height=8}
BGvalue_timeDaytable
#heatmap
#heatmaps
executeSavedPlot(data = allData, plotName = "meanBGheat_hist", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)

```

##Sensor value by time and date with mean values
```{r, eval=TRUE,fig.width=10, fig.height=8}
SGvalue_timeDaytable
#heatmap
#heatmaps
executeSavedPlot(data = allData, plotName = "meanSGheat_hist", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)

```



##Interactive Plots
###linePlots
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, plotName = "lineSumSens_SGper_Sett_BG", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "lineSumSens_BGper_Sett_BG", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "lineSumSens_BGper_subCarb_BG", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "lineSumSens_BGper_subCarb_Sett_BG", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)

```

###barplots hourly
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, plotName = "sumBar_highBG150_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "sumBar_lowBG80_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "stackBarInsulinHour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "stackBarBGallHour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
```

###every 3 hours barplots
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, plotName = "stackBarBG3Hour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "stackBarInsulin3Hour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
```
###daily barplots
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, plotName = "stackBarInsulinDaily", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "stackBarBGDaily", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "stackBarSGDaily", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
```

###boxplots hourly
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, plotName = "boxSGhour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "boxBGhour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "boxCorrUhour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "boxFoodUhour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)

```

###3hour boxplots
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, plotName = "boxSG3hour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "boxBG3hour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "boxCorrU3hour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "boxFoodU3hour_Sett", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
```

###daily boxplots
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, plotName = "boxSGdaily", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
executeSavedPlot(data = allData, plotName = "boxBGdaily", libraryPath = libraryPath,
                 numberDays = numberDays,changeParam.list = changeParam.list)
```
