---
title: "BG_report"
author: "Lillian Gorman Sanisaca, lgormansanisaca@usgs.gov"
date: "Created 9/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.width=12, fig.height=8, warning = FALSE)
```

#BG Report
Data import and tables
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
#setPaths
libraryPath<-"F:/BG.library_repos/BG.library/"
path<-"F:/BG.library_repos/"
fileName<-"CareLink-Export-1569716195944.csv"
numberDays<-5

#load functions
devtools::load_all(libraryPath,recompile = FALSE) 

#get pumpSettings
pumpSettings.list<-makePumpSettings(libraryPath)
unPackList(lists = list(pumpSettings.list = pumpSettings.list),
           parentObj = list(NA)) 

#metronic csv data import
dataImport.list<-dataImport(path,fileName)
unPackList(lists = list(dataImport.list = dataImport.list),
           parentObj = list(NA)) 

#summarize data
BGvalue_Summary<-summarizeData(allData, colName = "BG.Reading..mg.dL.", numberDays = numberDays)
BGvalue_SummaryDaily<-summarizeData(allData, colName = "BG.Reading..mg.dL.", numberDays = 7, timeStep = "day")
Sensorvalue_Summary<-summarizeData(allData, colName = "Sensor.Glucose..mg.dL.", numberDays = numberDays)
BGHigh_Count<-summarizeData(allData, colName = "BG.Reading..mg.dL.", numberDays = numberDays,
                            sumFuncs = "length",
                            filterCond = "data[data$BG.Reading..mg.dL.>150 & !is.na(data$BG.Reading..mg.dL.),]")
BGveryHigh_Count<-summarizeData(allData, colName = "BG.Reading..mg.dL.", numberDays = numberDays,
                                sumFuncs = "length",
                                filterCond = "data[data$BG.Reading..mg.dL.>300 & !is.na(data$BG.Reading..mg.dL.),]")

BGLow_Count<-summarizeData(allData, colName = "BG.Reading..mg.dL.", numberDays = numberDays,
                           sumFuncs = "length",
                           filterCond = "data[data$BG.Reading..mg.dL.<80 & !is.na(data$BG.Reading..mg.dL.),]")
BGgood_Count<-summarizeData(allData, colName = "BG.Reading..mg.dL.", numberDays = numberDays,
                            sumFuncs = "length",
                            filterCond = "data[data$BG.Reading..mg.dL.>=80 & data$BG.Reading..mg.dL.<=150 & !is.na(data$BG.Reading..mg.dL.),]")
tempBasal_count<-summarizeData(allData, colName = "Temp.Basal.Amount", numberDays = 7,
                               sumFuncs = "length",
                               filterCond = "data[data$Temp.Basal.Amount==0 & !is.na(data$Temp.Basal.Amount),]")
suspendBasal_Count<-summarizeData(allData, colName = "Alarm", numberDays = numberDays,
                                  sumFuncs = "length",
                                  filterCond = "data[regexpr('SUSPEND',data$Alarm)>0 & !is.na(data$Alarm),]")


#timeDayTables used for heatmaps
BGvalue_timeDaytable<-timeDayTable(allData, tcol = "time2", dcol = "Date2", 
                                   valueVar = "BG.Reading..mg.dL.", 
                                   sumFunc = "mean", naRemove = TRUE,
                                   includeTotals = TRUE,
                                   numberDays = numberDays, filterCond = "")
Sensorvalue_timeDaytable<-timeDayTable(allData, tcol = "time2", dcol = "Date2", 
                                       valueVar = "Sensor.Glucose..mg.dL.", 
                                       sumFunc = "mean", naRemove = TRUE,
                                       includeTotals = TRUE,
                                       numberDays = numberDays, filterCond = "")
carbs_timeDaytable<-timeDayTable(allData, tcol = "time2", dcol = "Date2", 
                                 valueVar = "BWZ.Carb.Input..grams.", 
                                 sumFunc = "max", naRemove = TRUE,
                                 includeTotals = TRUE,replaceNAs = TRUE,
                                 numberDays = numberDays, filterCond = "")
```

##BG value stats by hour
```{r, eval=TRUE}
BGvalue_Summary
```
##BG value stats by day
```{r, eval=TRUE}
BGvalue_SummaryDaily
```

##Sensor value stats by hour
```{r, eval=TRUE}
Sensorvalue_Summary
```

##BG high>150 count
```{r, eval=TRUE}
BGHigh_Count
```

##BG very high count
```{r, eval=TRUE}
BGveryHigh_Count
```

##BG low count
```{r, eval=TRUE}
BGLow_Count
```

##BG good value count (>80 and <150)
```{r, eval=TRUE}
BGgood_Count
```

##Temp Basal = 0 count past 7 days
```{r, eval=TRUE}
tempBasal_count
```

##Suspend basal on low count
```{r, eval=TRUE}
suspendBasal_Count
```


##BG value by time and date with mean values
```{r, eval=TRUE,fig.width=14, fig.height=10}
BGvalue_timeDaytable
#heatmap
heatMap(BGvalue_timeDaytable, hasTotals = TRUE,
        margins = c(6,20), brks = seq(0,450,50), 
        brewerPallete = "RdBu")
```

##Sensor value by time and date with mean values
```{r, eval=TRUE,fig.width=14, fig.height=10}
Sensorvalue_timeDaytable
#heatmap
heatMap(Sensorvalue_timeDaytable, hasTotals = TRUE,
        margins = c(6,20), brks = seq(0,450,50), 
        brewerPallete = "RdBu")
```



##Interactive Plots
###linePlots
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, numberDays = 5, plotName = "lineSumSens_SGper_Sett_BG", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "lineSumSens_BGper_Sett_BG", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "lineSumSens_BGper_subCarb_BG", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "lineSumSens_BGper_subCarb_Sett_BG", libraryPath)

```

###barplots hourly
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, numberDays = 5, plotName = "sumBar_highBG150_Sett", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "sumBar_lowBG80_Sett", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "stackBarInsulinHour_Sett", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "stackBarBGallHour_Sett", libraryPath)
```

###every 3 hours barplots
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, numberDays = 5, plotName = "stackBarBG3Hour_Sett", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "stackBarInsulin3Hour_Sett", libraryPath)
```
###daily barplots
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, numberDays = 5, plotName = "stackBarInsulinDaily", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "stackBarBGDaily", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "stackBarSGDaily", libraryPath)
```

###boxplots hourly
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, numberDays = 5, plotName = "boxSGhour_Sett", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "boxBGhour_Sett", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "boxCorrUhour_Sett", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "boxFoodUhour_Sett", libraryPath)

```

###3hour boxplots
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, numberDays = 5, plotName = "boxSG3hour_Sett", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "boxBG3hour_Sett", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "boxCorrU3hour_Sett", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "boxFoodU3hour_Sett", libraryPath)
```

###daily boxplots
```{r, eval=TRUE, echo=FALSE,warning=FALSE}
executeSavedPlot(data = allData, numberDays = 5, plotName = "boxSGdaily", libraryPath)
executeSavedPlot(data = allData, numberDays = 5, plotName = "boxBGdaily", libraryPath)
```